### 2015-05-27 test-proto.tex
test protocols

\subsection{ARM DS-5 Streamline}
% Use a daemon and a driver to get system info and send them to another machine. Has almost no impact on the performance and the load of the system.

@@

For the IPsec use case, the cipher/authentication pair null/null will be used to quantify the overhead of the encapsulation.
It should however not be forgotten that it is not to be used as a production configuration.
As the RFC 7321~\citep[pg. 7]{rfc7321} sates: ``Note that while authentication and encryption can each
   be `NULL', they MUST NOT both be `NULL'".

We will also use two types of drivers for the BA411E: an interuption-based for OpenVPN and OpenSSH, and a polling-based for IPsec.

@@

>>>>

\subsection{ARM DS-5 Streamline}
Streamline is a toolsuite included in ARM Development Studio.
By installing a kernel module and running a daemon on the board, it can fetch a huge amount of data without over-loading the system.
This tool is able to gather information on the CPU utilisation, the amount of context switches, of interrupts, of memory used, and much more.
If the applications, libraries and kernel modules have been compiled with the required debugging options, it can also build the call path of a run, giving extensive statistics on the most ressource-hungry functions.

If it has close to no impact on the performance of the board, the same does not go for the hosting machine.
A serious drawback is his memory consumption that, when combined with the ressources used by the virtual machine, bring the hosting machine to its knees.

\noindent The user should also be aware that if Streamline if a very powerfull and versatile tool, it is not reliable at very high resolution.
The data should not be analyzed in windows smaller than a millisecond.

\section{Test cases}
The aim of this work is to test the implementations under realistic situations.
To reach this goal, three test cases will be used:
\begin{itemize}
	\item Lots of connections without fetching any data.
	\item Latency of the connection. This test can also illustrate the transfer of small amount of data.
	\item Large file transfer on an established connection.
\end{itemize}

Each of those tests will go from a raw run, without any encryption nor authentication serving as a comparison ground, gradually increasing security up to a complete encryption/authentication scheme.

\noindent As AES mode CBC and SHA-2 are widely used, they will be used with a serious security paramter using keys of 256-bit.
Some test case will also experiment some implementation of AES-GCM to compare its performance and justify the need for its offloading in hardware.

For the IPsec and OpenVPN implementation, the cipher/authentication pair null/null will be used to quantify the overhead of the encapsulation.
It should however not be forgotten that it is not to be used as a production configuration.
As the RFC 7321~\citep[pg. 7]{rfc7321} sates for IPsec: ``Note that while authentication and encryption can each
   be `NULL', they MUST NOT both be `NULL'".

We will use two types of drivers for the BA411E: an interuption-based for OpenVPN and OpenSSH, and a polling-based for IPsec.

@@

@@

All the results on the throughput and CPU usage take into account only the file transfer.
The server authentication, the connection establishement and any other securoty negociation is ignored in this particular test case.
